---
title: "Bayer Business Intelligence Analysis"
subtitle: "Focus: Manufacturer 1"
author: "Camilla Yu"
output: pdf_document
---

```{r setup, include=FALSE}
library(readxl)
library(tidyverse)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggstatsplot)
library(GGally)
library(ggpubr)
```

```{r, echo=FALSE}
data <- read_excel("bayer intern2.xlsx")
data <- as.data.frame(data)
```

```{r, echo=FALSE}
data <- data %>% 
  select(-Market) %>%
  mutate(dollar = `Dollar Sales`,
         dollar_last = `Dollar Sales Year Ago`) %>%
  select(-c(`Dollar Sales`, `Dollar Sales Year Ago`))
```

```{r, echo=FALSE}
data_part <- data[3:nrow(data),]
```

## Background 

For this report, there are two types of categories: analgesics and upper 
respiratory. Manufacturers include MFC 1, MFC 2, MFC 3, MFC 4, MFC 5, MFC 6 and 
MFC 7 with many different brands. Based on the data, we have dollar sales as
well as dollar sales in the last year. The report is separated into three 
parts: 1.General glimpse for the whole market, 2.Manufacture 1 (MFR 1)'s 
performance compared to the market, and 3.Market share in this year and last 
year. 

## 1. General glimpse for the whole market

We could make separate histograms for analgesics and upper respiratory with colors
indicating different years. 

```{r, echo=FALSE}
analgesics <- data_part %>% filter(Category == "ANALGESICS")
upper <- data_part %>% filter(Category == "UPPER RESPIRATORY")
```

```{r, echo=FALSE}
dollar <- data.frame(dollar = analgesics$dollar, type = "This Year", manufacturer = analgesics$Manufacturer)
dollar_last <- data.frame(dollar = analgesics$dollar_last, type = "Last Year", manufacturer = analgesics$Manufacturer)
analgesics_dollar <- rbind(dollar, dollar_last)
analgesics_dollar <- analgesics_dollar %>%
  mutate(dollar = round(dollar/1000000), n = 2)
```

```{r, echo=FALSE}
p1 <- ggplot(analgesics_dollar, aes(x = manufacturer, y = dollar, fill = type)) +
  geom_bar(position=position_dodge(), stat = "identity", colour = "black") +
  labs(title = "Dollar Sales for Analgesics",
       x = "Manufacturer",
       y = "Dollar in hundred thousand") +
  theme(plot.title = element_text(hjust=0.5))
```

```{r, echo=FALSE}
dollar <- data.frame(dollar = upper$dollar, type = "This Year", manufacturer = upper$Manufacturer)
dollar_last <- data.frame(dollar = upper$dollar_last, type = "Last Year", manufacturer = upper$Manufacturer)
upper_dollar <- rbind(dollar, dollar_last)
upper_dollar <- upper_dollar %>%
  mutate(dollar = round(dollar/1000000), n = 2)
```

```{r, echo=FALSE}
p2 <- ggplot(upper_dollar, aes(x = manufacturer, y = dollar, fill = type)) +
  geom_bar(position=position_dodge(), stat = "identity", colour = "black") +
  labs(title = "Dollar Sales for Upper Respiratory",
       x = "Manufacturer",
       y = "Dollar in hundred thousand") +
  theme(plot.title = element_text(hjust=0.5))
```

```{r, fig.width=9, fig.height=3, echo=FALSE}
ggarrange(p1, p2, ncol = 2, nrow = 1)
```

Based on the plot, we could have a general sense that dollar sales for upper respiratory 
are better than it for analgesics. And for analgesics, dollar sales in this year 
for most of the manufacturers increase compared to it in the last year. But for
upper respiratory, dollar sales in this year for roughly half of the manufacturers
decrease compared to it in the last year. We could research more about the 
decreasing trend in dollar sales for upper respiratory to capture the future 
trend and make adjustments for better adapting the market. 

- For analgesics, MFR 3 has the highest dollar sales in both this year and last
year, followed by MFR 2. MFR 1 did better than half of the manufactures, and
MFR 1, MFR 2 and MFR 3 have two different brands for analgesics.

- For upper respiratory, MFR 5 has the highest dollar sales in this year, while
MFR 6 has the highest dollar sales in the last year, followed by MFR 1 and MFR 3.

- MFR 1 did better than roughly 75% of the manufactures. MFR 3 and MFR6 have 
two different brands for upper respiratory.


```{r, echo=FALSE}
MFR1_this <- data.frame(type = "This Year", dollar = c(261, 198), brand = c("MFR 1 Brand 3", "MFR 1 Brand 5"))
MFR1_last <- data.frame(type = "Last Year", dollar = c(285, 192), brand = c("MFR 1 Brand 3", "MFR 1 Brand 5"))
MFR1_analgesics <- rbind(MFR1_this, MFR1_last)
```

```{r, echo=FALSE}
is_outlier <- function(x) {
  return(x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x))
}

dat <- analgesics_dollar %>% tibble::rownames_to_column(var="outlier") %>% group_by(type) %>% mutate(outlier=ifelse(is_outlier(dollar), manufacturer, as.numeric(NA)))

p3 <- ggplot(dat, aes(y=dollar, x=type, fill = type)) + geom_boxplot() + geom_text(aes(label=outlier),na.rm=TRUE,hjust=0.5, vjust=-0.5, size=3) +
  labs(title = "Analgesics Dollar Sales", 
            y = "Dollar in hundred thousand",
            x = "") +
  geom_point(data = MFR1_analgesics, aes(x= type, y = dollar), color = "blue") +
  geom_text(data = MFR1_analgesics, aes(label = brand), color = "blue",
            hjust=0.5, vjust=-1, size=3) +
  theme(plot.title = element_text(hjust=0.5))
```

```{r, echo=FALSE}
upper_this <- data.frame(dollar = upper$dollar, type = "This Year", manufacturer = analgesics$Manufacturer)
upper_last <- data.frame(dollar = upper$dollar_last, type = "Last Year", manufacturer = analgesics$Manufacturer)
upper_dollar <- rbind(upper_this, upper_last)
upper_dollar <- upper_dollar %>%
  mutate(dollar = round(dollar/1000000), n = 2)
```

```{r, echo=FALSE}
MFR1_this <- data.frame(type = "This Year", dollar = 511, brand = "MFR 1 Brand 13")
MFR1_last <- data.frame(type = "Last Year", dollar = 481, brand = "MFR 1 Brand 13")
MFR1_analgesics <- rbind(MFR1_this, MFR1_last)
```

```{r, echo=FALSE}
is_outlier <- function(x) {
  return(x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x))
}

dat <- upper_dollar %>% tibble::rownames_to_column(var="outlier") %>% group_by(type) %>% mutate(outlier=ifelse(is_outlier(dollar), manufacturer, as.numeric(NA)))

p4 <- ggplot(dat, aes(y=dollar, x=type, fill = type)) + geom_boxplot() + geom_text(aes(label=outlier),na.rm=TRUE,hjust=0.5, vjust=-0.5, size=3) +
  labs(title = "Upper Respiratory Dollar Sales", 
            y = "Dollar in hundred thousand",
            x = "") +
  geom_point(data = MFR1_analgesics, aes(x= type, y = dollar), color = "blue") +
  geom_text(data = MFR1_analgesics, aes(label = brand), color = "blue",
            hjust=0.5, vjust=-1, size=3) +
  theme(plot.title = element_text(hjust=0.5))
```


## 2. Manufacture 1 (MFR 1)'s performance compared to the market

### Analgesics:

```{r, echo=FALSE}
upper <- upper %>%
  mutate(perc = round((dollar - dollar_last)/dollar_last * 100, 2))
analgesics <- analgesics %>%
  mutate(perc = round((dollar - dollar_last)/dollar_last * 100, 2))
data <-rbind(upper, analgesics) %>% 
  mutate(category = as.character(tolower(Category)))
```

```{r, echo=FALSE}
MFR1_ana <- data.frame(category = "analgesics", perc = c(round((260846516 - 284658263)/284658263*100, 2), round((197902438 - 191812842)/191812842*100, 2)), brand = c("MFR 1 Brand 3", "MFR 1 Brand 5"))
MFR1_upper <- data.frame(category = "upper respiratory", perc = round((510499642 - 481175624)/481175624*100, 2), brand = "MFR 1 Brand 13")
MFR1_perc <- rbind(MFR1_ana, MFR1_upper)
```

```{r, echo=FALSE}
dat <- data %>% tibble::rownames_to_column(var="outlier") %>% mutate(outlier=ifelse(is_outlier(perc), Manufacturer, as.numeric(NA)))

p5 <- ggplot(dat, aes(y=perc, x=category, fill = category)) + geom_boxplot() + geom_text(aes(label=outlier),na.rm=TRUE,hjust=0.5, vjust=-0.5, size=3) +
  labs(title = "Sales Growth Rate", 
            y = "Growth rate in percentage",
            x = "") + 
  geom_point(data = MFR1_perc, aes(x= category, y = perc), color = "blue") +
  geom_text(data = MFR1_perc, aes(label = brand), color = "blue",
            hjust=0.5, vjust=-1, size=3) +
  theme(plot.title = element_text(hjust=0.5))
```

```{r, echo=FALSE}
p3
```

- In general, MFR 1 did a great job since no matter for which brand or year, 
the dollar sales are above the median compared to the whole market.

- For MFR 1, dollar sales for brand 3 are larger than it for brand 5. So, MFR 1 
could research more about the differences between two brands to improve the 
performance for brand 5.

- MFR 3 and MFR 2 did a weigh better job than the rest of the market, MFR 1 could 
study from them and improve two brands.

- For MFR 1, brand 5 sold more in this year while brand 3 sold less compared to 
it in the last year, MFR 1 could research the reasons for increasing trend for 
brand 5 to increase dollalr sales for brand 3 and keep the increasing trend for 
both two brands.

- The gap for the whole market in this year decreases compared to it in the last
year. MFR 1 could study more about the trend for the whole market and adapt to
it in the future. For this year, the market for analgesics seems to be more
competitive than the last year. 

### Upper Respiratory:

```{r, echo=FALSE}
p4
```

- MFR 1's dollar sales for upper respiratory are above 75% of the manufacturers 
no matter for this year or last year and did a great job. 

- The 75% percentile for dollar sales for the whole market 
in this year increases compared to it in the last year but the gap or difference 
between manufacturers in dollar sales for this year increases. And it's beneficial 
to think about the reason behind the fact so that MFR 1 could improve the 
performance while avoiding the decreasing trend. 

- For MFR 1, the dollar sales for upper respiratory in this year is larger than 
it in the last year, and if MFR 1 could investigate the reason for increasing 
sales, it might be useful for later successes. 

### Growth Rate

```{r, echo=FALSE}
p5
```

- For both analgesics and upper respiratory, more than half of the 
manufacturers have positive growth rate in dollar sales.

- In general, the median growth rate for upper respiratory is larger than it for
analgesics. If MFR 1 could research the reason for why the growth rate is larger
for upper respiratory, they could have more successful strategies or design 
more products which cater to the market demand. 

- Based on the plot, we could confirm the findings from previous sections that 
brand 5 for analgesics and brand 13 for upper respiratory have positive growth 
rate, while brand 3 for analgesics has negative growth rate. So, MFR 1 needs to 
investigate the reason for negative growth rate and learn from it to avoid it in 
the future.

- It's also beneficial to learn cases from MFR 6 to avoid such a large negative
growth rate in the future.

## 3. Market share in this year and last year

```{r, echo=FALSE}
data <- read_excel("bayer intern2.xlsx")
data <- as.data.frame(data)
```

```{r, echo=FALSE}
data <- data %>% 
  select(-Market) %>%
  mutate(dollar = `Dollar Sales`,
         dollar_last = `Dollar Sales Year Ago`) %>%
  select(-c(`Dollar Sales`, `Dollar Sales Year Ago`))
```

```{r, echo=FALSE}
pie_ana <- data %>% filter(Category == "ANALGESICS") %>%
  group_by(Manufacturer) %>%
  summarise(dollar = sum(dollar),
            dollar_last = sum(dollar_last))
```

```{r, echo=FALSE}
pie_ana_this <- pie_ana %>% arrange(desc(dollar)) %>%
  mutate(prop = round(dollar / sum(dollar) *100, 1))
```

```{r, echo=FALSE}
pie_ana_last <- pie_ana %>% arrange(desc(dollar_last)) %>%
  mutate(prop = round(dollar_last / sum(dollar_last) *100, 1))
```

```{r, echo=FALSE}
pie_ana_plot <- ggplot(pie_ana_this, aes(x="", y=prop, fill=Manufacturer)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() +
  labs(title = " This Year") +
  scale_fill_brewer(palette="Set1") +
  theme(plot.title = element_text(hjust=0.5))
pie_ana_last <- ggplot(pie_ana_last, aes(x="", y=prop, fill=Manufacturer)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() +
  labs(title = "Last Year") +
  scale_fill_brewer(palette="Set1") +
  theme(plot.title = element_text(hjust=0.5))
plot<- ggarrange(pie_ana_plot,pie_ana_last,ncol=2, nrow=1, common.legend = TRUE,legend="bottom")
annotate_figure(plot, top = text_grob("Sales Proportion for Analgesics", 
               color = "black", face = "bold", size = 14))
```

- The market share for analgesics in this year and last year are pretty similar.

- All other manufacturers has the largest market share for analgesics and that
makes sense since the category might include many manufacturers together.

- MFR 3 has the second largest market share for analgesics, followed by MFR 2
and MFR 1. Learning from MFR 3 might be beneficial for MFR 1.

```{r, echo=FALSE}
pie_upper <- data %>% filter(Category == "UPPER RESPIRATORY") %>%
  group_by(Manufacturer) %>%
  summarise(dollar = sum(dollar),
            dollar_last = sum(dollar_last))
```

```{r, echo=FALSE}
pie_up_this <- pie_upper %>% arrange(desc(dollar)) %>%
  mutate(prop = dollar / sum(dollar) *100)
```

```{r, echo=FALSE}
pie_up_last <- pie_upper %>% arrange(desc(dollar_last)) %>%
  mutate(prop = dollar_last / sum(dollar_last) *100)
```

```{r, echo=FALSE}
pie_up_plot <- ggplot(pie_up_this, aes(x="", y=prop, fill=Manufacturer)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() +
  labs(title = " This Year") +
  scale_fill_brewer(palette="Set1") +
  theme(plot.title = element_text(hjust=0.5))
pie_up_last <- ggplot(pie_up_last, aes(x="", y=prop, fill=Manufacturer)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() +
  labs(title = "Last Year") +
  scale_fill_brewer(palette="Set1") +
  theme(plot.title = element_text(hjust=0.5))
plot<- ggarrange(pie_up_plot,pie_up_last,ncol=2, nrow=1, common.legend = TRUE,legend="bottom")
annotate_figure(plot, top = text_grob("Sales Proportion for Upper Respiratory", 
               color = "black", face = "bold", size = 14))
```

- The findings of market share for upper respiratory are pretty similar to what
I found in market share for analgesics.

- Except for all other manufacturers, the market share for the rest of 
manufacturers are pretty even, which might indicate that the market is competitive
for upper respiratory. Learning from other manufacturers or dig into the reasons
for competitive market might be beneficial for MFR 1. 